Simulating an Isolated Dwarf Galaxy with Multi-Channel Feedback and Chemical Yields from Individual Stars

### 2018-08-20 main.tex
mostly done with updates.. a little more

\setcounter{figure}{0}
\section{H$^{-}$ Photodetachment}
\label{appendix:H minus}
\textbf{As discussed in Section~\ref{sec:molecular gas content}, H$_2$ formation is dominated by the gas-phase H$^{-}$ channel in our simulations. Accounting for the photodetachment of H$_{-}$ from the stellar radiation field, which can dominate over the UVB, is potentially important for correctly modeling H$_2$ formation in low metallicity gas\citep{WolcottHaiman2012}. In addition, radiation from lower mass stars may be important in the is regime as the H$^{-}$ photodetachment threshold is low, or 0.76~eV. }

>>>>

\setcounter{figure}{0}
\section{H$^{-}$ Photodetachment}
\label{appendix:H minus}
\textbf{As discussed in Section~\ref{sec:molecular gas content}, H$_2$ formation is dominated by the gas-phase H$^{-}$ channel in our simulations. Accounting for the photodetachment of H$_{-}$ from the stellar radiation field, which can dominate over the UVB,can be important for correctly modeling H$_2$ formation in low metallicity gas\citep{WolcottHaiman2012}. To test the significance of this radiation in determining the final H$_2$ mass we run a grid of one-zone Grackle cooling models\footnote{See the ``cooling_cell.py'' example here: https://grackle.readthedocs.io/en/grackle-3.1/Python.html} that iterates through the chemistry and cooling solvers with a constant density (10~cm$^{-3}$). In Fig.~\ref{fig:Grackle grid} we plot the final H$_2$ mass fraction in these cells for variations over five orders of magnitude in the adopted H$^{-}$ photodetachment rate and the Lyman-Werner radiation background. As shown, the H$_2$ mass fraction is much more sensitive to the Lyman-Werner radiation field than the H$^-$ photodetachment rate. In effect, our simulations move left-to-right in this diagram (only) as stars form (right) or die (left). A complete model, including the stellar contribution to H$^{-}$ photodetachment, would move somewhat diagonally.}

\textbf{We follow up on the qualitative conclusions of these models by running four full-physics simulations, but with no star formation, at the four points starred in the diagram. These vary the radiation bands by factors of 100 each, which is comparable to the ratio between the typical ISRF and the UVB in the disk of our galaxy (see Fig.~\ref{fig:ISRF}). Changing the background H$^{-}$ photodetachment rate by a factor of 100 only (top left star) leads to a reduction in the final H$_2$ mass fraction by 3, while changing the Lyman-Werner background by a factor of 100 (bottom right point) decreases the H$_2$ mass by a factor of 6.9. Applying both scale factors gives a reduction of 7.9.}

\begin{figure}
\centering
\includegraphics[width=0.95\linewidth]{fH2.png}
\caption{The final H$_2$ mass fraction in a grid of one-zone Grackle cooling models run with the same Grackle parameters and metallicity as our full hydrodynamics simulation. Each model is held at a uniform density $n = 10$~cm$^{-3}$. Each model varies either the H$^{-}$ photodetachment rate or the Lyman-Werner background over their respective UVB values by a given scale factor. Contours give factors of ten change in the H$_2$ fraction.}
\label{fig:Grackle grid}
\end{figure}

\textbf{H$^-$ photodetachment arises from lower energy photons, above 0.76~eV, with a peak in effectiveness around 2~eV. For this reason, low mass stars may contribute significantly, if not dominate, the radiation field responsible for this reaction. Although we demonstrate that the H$_2$ fraction is more sensitive to the Lyman-Werner radiation field in our simulations, this radiation is dominated by short-lived massive stars and thus subject to fluctuations. Particularly in periods of no star formation, the regulation of H$^-$ photodetachment from low energy photons may play a non-negligible role in regulating H$_2$ formation. Indeed there is H$_2$ growth during these periods due to a decrease in the Lyman-Werner field, but it is unclear how much of this would be attenuated by accounting for photons from lower mass stars. Doing so in our current model, applying an optically thin 1/r$^2$ field for each star, would be computationally challenging for the dramatic increase in the number of stars below 8~M$_{\odot}$, our current radiation mass threshold.}

In addition, radiation from lower mass stars may be important in the is regime as the H$^{-}$ photodetachment threshold is low, or 0.76~eV. }
